Price of Anarchy for Mean Field Games

### 2018-07-28 PoA.tex
minor change prop 6 remove assumption b1 bar > 0
update prop 5 return back to previous version

	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.
	Note that $D^{r \to \infty}_u > 0$ and $\lim_{r \to \infty} B^{r}(D^{r,u})^2 + 2 A^u D^{u,r} - C^{u,r} = \infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) we know that for all large $r$, the function $ t \mapsto u_t^{r}$ is increasing. Moreover, there exists $r^*>0$ such that for all $r \geq r^*$ and all $t \in [0,T]$,
	$$ 0 \leq u_t^{r} \leq u_T^{r}  = D^{u,r} \leq D^{r\to \infty}_u + 1.$$

%	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
%	\begin{equation*}
%	\begin{split}
%	\left\vert u_t^{r} \right\vert&=\frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \\
%	& \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} \\
%	&\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } := c_2.
%	\end{split}
%	\end{equation*}

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded for $t \in [0,T]$, which comes from the fact that $u^r_t \geq 0$ for all $t \in [0,T]$ so that,
	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T]. $$  	
	Similarly, for every $t\in [0,T]$,
	$$\lim_{r\to \infty}w^r_t =: w_t^{r\to \infty},\qquad \lim_{r\to \infty} \eta^r_t =: \eta_t^{r\to \infty},$$
	and the functions $w^{r}_t$ and $\eta^{r}_t$ are uniformly bounded over $t \in[0,T]$ and large $r$. By the bounded convergence theorem we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{MFG,r})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{MFG,r\to \infty})^2 dt \  < \infty,
	\end{equation*}
	and thus,
	\begin{equation*}
	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot B^r\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{MFG,r})^2 dt = 0.
	\end{equation*}

@@

	\textbf{Case 2:} Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have:
	\begin{equation*}
	\begin{array}{l}
		\lambda \longrightarrow 0\\
		\displaystyle B^{b_2} \longrightarrow{}  \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{b_2 \to 0} >0, \qquad B^{\eta,b_2} \longrightarrow{} 0 \\
		C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0,
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, C^\eta, D^\eta)$ are independent of $b_2$.
	Moreover, we have $\lim_{b_2 \to 0}\delta^{+,b_2}_u =-2A^u >0 $ and $\lim_{b_2 \to 0}\delta^{-,b_2}_u = 0$, so that $\lim_{b_2 \to 0}(\delta^{+}_u - \delta^{-}_u) = -2 A^u > 0$. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
	$$\lim_{b_2 \to 0}u^{b_2}_t = 0 .$$
	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough. Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 < b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
	\begin{equation*}
	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2 ,\qquad \forall  \  t \in [0,T]
	\end{equation*}

@@

\begin{proof}	
	\textbf{Case 1: } When $\bar{b}_2 \to 0$, we have:
	\begin{equation*}
	\begin{array}{l}
		 \lambda^{\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}, \qquad 
		 B^{\bar{b}_2} \to \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{\bar{b}_2 \to 0} > 0,\\
		 C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{\bar{b}_2 \to 0}_u >0,\qquad 
		 D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{\bar{b}_2 \to 0}_u \geq 0,
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.	
	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
	\begin{equation}
	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} +B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
	\end{equation}
	which we recall has an explicit solution. It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$. Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}. Because $\bar{b}_1 > 0$, we have $A^u < 0$. For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$. Thus, for all $\bar{b}_2<\bar{b}^*_2$ and for every $t \in [0,T]$:
	\begin{equation*}
		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}} =:c_2.
	\end{equation*}

>>>>

%	Note that $D^{r \to \infty}_u > 0$ and $\lim_{r \to \infty} B^{r}(D^{r,u})^2 + 2 A^u D^{u,r} - C^{u,r} = \infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) we know that for all large $r$, the function $ t \mapsto u_t^{r}$ is increasing. Moreover, there exists $r^*>0$ such that for all $r \geq r^*$ and all $t \in [0,T]$,
%	$$ 0 \leq u_t^{r} \leq u_T^{r}  = D^{u,r} \leq D^{r\to \infty}_u + 1.$$
	Next, our goal is to bound the $u^r_t$ uniformly over $t \in [0,T]$ for large enough $r$.
	Note that  $A^u < 0$, $B^r$, $C^{u,r}$, $\lambda^{r\to \infty}$, $C^{r \to \infty}_u>0$, $D^{u,r}$, $D^{r \to \infty}_u\geq 0$, and $\delta^{-,r}_u < 0 < \delta^{+,r}_u$. Let $\epsilon>0$. Then there exists $r^*>0$ such that $\max_{r > r^*}\{ B^{r}, C^{u,r}, D^{u,r} \} \leq \max\{C^{r \to \infty}_u,D^{r \to \infty}_u \}+\epsilon=: c_1$. Thus, we can deduce that for $r>r^*$, for every $t \in [0,T]$:
%	\begin{equation*}
%	\begin{split}
%	\left\vert u_t^{r} \right\vert &=\frac{C^{u,r} (1 -  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} ) + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u  e^{- (\delta^{+,r}_u - \delta^{-,r}_u) (T-t)} )}{D^{u,r} B^r (1 - e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}) + \delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)} - \delta^{-,r}_u} \\
%	& \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} \\
%	&\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2.
%	\end{split}
%	\end{equation*}
	\begin{equation}
	\left\vert u_t^{r} \right\vert \leq \frac{C^{u,r} + D^{u,r} (\delta^{+,r}_u - \delta^{-,r}_u)}{\delta^{+,r}_u e^{- (\delta^{+,r}_u - \delta^{-,r}_u)(T-t)}} 
	\leq  \frac{ c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}  }{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } }
	\end{equation}	
	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}) and by the bounded convergence theorem, we have for every $t \in [0,T]$:
	\begin{equation*}
		\lim_{r\to \infty}\bar{x}_t^{MFG,r} = \mathbb{E}(\xi) e^{(b_1+ \bar{b}_1)t} =: \bar{x}_t^{MFG,r\to \infty}.
	\end{equation*}
	Moreover, $\bar{x}_t^{MFG,r}$ is uniformly bounded for $t \in [0,T]$, which comes from the fact that $u^r_t \geq 0$ for all $t \in [0,T]$ so that,
	$$ \left\vert \bar{x}^{MFG,r}_t \right\vert \leq \vert \mathbb{E}(\xi) \vert e^{ (b_1 + \bar{b}_1 ) T }, \quad \forall t \in [0,T]. $$  	
	Similarly, for every $t\in [0,T]$,
	$$\lim_{r\to \infty}w^r_t =: w_t^{r\to \infty},\qquad \lim_{r\to \infty} \eta^r_t =: \eta_t^{r\to \infty},$$
	and the functions $w^{r}_t$ and $\eta^{r}_t$ are uniformly bounded over $t \in[0,T]$ and large $r$. By the bounded convergence theorem we have for every $t \in [0,T]$:
	\begin{equation*}
	\lim_{r \to \infty} \int_0^T (u^r_t - w^r_t)^2 (\bar{x}_t^{MFG,r})^2 dt = \int_0^T (u^{r \to \infty}_t- w^{r \to \infty}_t)^2 (\bar{x}_t^{MFG,r\to \infty})^2 dt \  < \infty,
	\end{equation*}
	and thus,
	\begin{equation*}
	\lim_{r \to \infty} \Delta SC^r = \lim_{r \to \infty} \frac{1}{2}\cdot B^r\int_0^T (u^r_t - w^r_t)^2 ( \bar{x}_t^{MFG,r})^2 dt = 0.
	\end{equation*}

@@

	\textbf{Case 2:} Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have:
	\begin{equation*}
	\begin{array}{l}
		\lambda \longrightarrow 0\\
		\displaystyle B^{b_2} \longrightarrow{}  \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{b_2 \to 0} >0, \qquad B^{\eta,b_2} \longrightarrow{} 0 \\
		C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0,
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, C^\eta, D^\eta)$ are independent of $b_2$.
	Moreover, we have $\lim_{b_2 \to 0}\delta^{+,b_2}_u =-2A^u >0 $ and $\lim_{b_2 \to 0}\delta^{-,b_2}_u = 0$, so that $\lim_{b_2 \to 0}(\delta^{+}_u - \delta^{-}_u) = -2 A^u > 0$. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
	$$\lim_{b_2 \to 0}u^{b_2}_t = 0 .$$
	Similar to Proposition \ref{prop:r_bar_r}, we can derive a uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough. Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 < b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
	\begin{equation*}
	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } ,\qquad \forall  \  t \in [0,T]
	\end{equation*}

@@

\begin{proof}	
	\textbf{Case 1: } When $\bar{b}_2 \to 0$, we have:
	\begin{equation*}
	\begin{array}{l}
		 \lambda^{\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0} := \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}, \qquad 
		 B^{\bar{b}_2} \to \frac{b_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{\bar{b}_2 \to 0} > 0,\\
		 C^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q+\bar{q}(1-s))=:C^{\bar{b}_2 \to 0}_u >0,\qquad 
		 D^{u,\bar{b}_2} \to \lambda^{\bar{b}_2 \to 0}(q_T+\bar{q}_T(1-s_T))=:D^{\bar{b}_2 \to 0}_u \geq 0,
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, B^\eta, C^\eta, D^\eta)$ are independent of $\bar{b}_2$.	
	Let $u^{\bar{b}_2 \to 0}:[0,T]\to \mathbb{R}$ be the solution to the limiting Riccati equation:
	\begin{equation}
	\left({u}^{{\bar{b}_2 \to 0}}_t\right)' - 2A^u u_t^{\bar{b}_2 \to 0} +B^{\bar{b}_2 \to 0} (u_t^{\bar{b}_2 \to 0})^2+ C^{\bar{b}_2 \to 0}_u = 0, \qquad u_T^{r \to \infty} = D^{\bar{b}_2 \to 0}_u,
	\end{equation}
	which we recall has an explicit solution. It is easy to show that for every time $t\in [0,T]$, $\lim_{\bar{b}_2 \to 0}u^{\bar{b}_2}_t=u^{\bar{b}_2 \to 0}_t$. Next, our goal is to bound $u^{\bar{b}_2}_t$ uniformly over $t \in [0,T]$ for small enough $\bar{b}_2$, following the methodology of the proof of Proposition \ref{prop:r_bar_r}. Because $b_1 > 0$, we have $A^u < 0$. For any $\epsilon>0$, there exists a $\bar{b}^*_2>0$ such that $\max_{\bar{b}_2<\bar{b}^*_2} \{ B^{\bar{b}_2},C^{u,\bar{b}_2},D^{u,\bar{b}_2} \}<\max \{B^{\bar{b}_2 \to 0},C^{\bar{b}_2 \to 0}_u,D^{\bar{b}_2 \to 0}_u \}+\epsilon=:c_1$. Thus, for all $\bar{b}_2<\bar{b}^*_2$ and for every $t \in [0,T]$:
	\begin{equation*}
		\left \vert u_t^{\bar{b}_2} \right\vert \leq \frac{c_1 + 2 c_1 \sqrt{(A^u)^2 + c_1^2}}{-2A^u e^{-2T \sqrt{(A^u)^2 + c_1^2}}}.
	\end{equation*}
